\subsubsection*{February 25, 2020}
\section{Constructing Finite Fields for Cryptography}
\subsection{Groups}
We've worked with groups: 
\begin{itemize}
	\item Subgroups
	\item Quotient groups
	\item Group homomorphisms
\end{itemize}
\begin{list}{$*$}{}  
	\item Lagrange's Thm
	\item Fundamental Homomorphism Theorem ($\nicefrac{G}{\ker \varphi}\cong \mathrm{im} \varphi$)
\end{list}
\begin{list}{$\circ$}{}  
	\item $\Z_n$
	\item Symmetry Groups
	\item Permutation Groups 
\end{list}

\subsection{Rings}
Ring = Abelian group + second operation.
\begin{itemize}
	\item Ideals (prime, maximal, principal)
	\item Quotient rings $\nicefrac{R}{I}$. 
	\item Ring homomorphisms. 
\end{itemize}
\begin{list}{$*$}{}  
	\item Fundamental homomorphism theorem for rings. 
	\item Connection between ideals and units. 
	\item Modding out a maximal ideal gives a field. 
	\item In a p.i.d., maximal ideals $\iff$ prime ideals. 
\end{list}

\subsection{Fields}
Fields = Abelian group under $+$ and $\times$. 
\begin{itemize}
	\item Take $F[x]$ (polynomials with coefficients in field $F$. 
	\item Take irreducible $p(x)\in F[x]$
	\item Construct $\nicefrac{F[x]}{\langle p(x)\rangle}$
\end{itemize}
This extends our collection f fields beyond $F_p$, $p$ prime and it allows for the extension of fields by ``adding'' roots of polynomials that weren't in the base field. 
\begin{list}{$\circ$}{}  
	\item Galois fields
\end{list}

\subsection{What will be on the test? }
\begin{itemize}
	\item Check definitions. (Checking that $\heartsuit$ is $\spadesuit$)
	\item Construct an isomorphism. (Show that $\heartsuit$ is isomorphic to $\spadesuit$)
	\item Construct a field by giving $+$ and $\times$ table. (``I raise you $\Z_p$ and $p(x)\in \Z_p[x]$, give me the field $(\Z_p)_{\langle p(x)\rangle}$!'')
\end{itemize}

\exercise Let $C_2$ be the subgroup $\{\pm 1\}$ of the multiplicative group $\R^\times$. Show that $\R^times$ is isomorphis to $\R^+ \times C_2$. 

We can construct isomorphism
\[\varphi: (x, u) \mapsto u\cdot e^x\qquad \varphi^{-1}:a\mapsto (\ln|a|, \mathrm{sgn}(a))\]
We check that is it a homomorphism first: 
\begin{align*}
	\varphi\big((x_1, u_1)\times (x_2, u_2)\big)&=\varphi\big((x_1+x_2, u_1u_2)\big) \\
	&=u_1u_2e^{x_1+x_2}=u_1e^{x_1}u_2e^{x_2} = \varphi\big((x_1,u_1)\big)\varphi\big((x_2,u_2)\big)
\end{align*}
1-1: Check that $\ker\varphi=\{(0,1)\}$

onto: Which input gives me $y\in \R^{\times}$? 
\[\varphi(\underbrace{\ln|a|}_{\in \R^+}, \underbrace{\mathrm{sgn}(a)}_{\in\{\pm 1\}}) = \mathrm{sgn}(y)\cdot |y| = y\implies\text{onto}\]
